Learning the local coding scheme: Jointly Optimized Locally Linear Classifiers

### 2017-09-11 paper/llncs2e/PKDD2017.tex
modify pic

\documentclass{llncs}
\usepackage[tbtags]{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tabu}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

@@

	Apart from local coding based methods, a number of other locally linear classifiers have been proposed. CSVM \cite{16} adopts K-means to partition the data into several clusters and then trains a linear SVM for each cluster. The key point of CSVM is that it requires each cluster's model to align with a global model, which can be treated as a kind of regularization. Different from CSVM, SVM-KNN \cite{17} employs a lazy learning strategy by training a linear SVM in the subregion of a testing sample and then use the trained SVM classifier for prediction.
	\section{Jointly Optimized Locally Linear Classifier}
	\subsection{Optimized Localized Soft-assignment Coding}
	Although localized soft-assignment coding  achieves a good balance between the local region constraint and sensitivity to the variance of distance, the number of nearest anchor points $k$ is commonly picked via cross-validation and fixed for the whole dataset. This strategy is based on the assumption that each data point shares similar local manifold. However, it is often the case that the dataset is generated from an unknown distribution which in turn leads to an unknown distributed anchor points, the local manifold may vary from data point to data point. In other words the optimum number of anchor points involved in the local coding is different for each data point as Figure 1 shows.
	\begin{figure}[!tbp]
		\centering
		\subfloat[]{\includegraphics[width=0.45\textwidth]{knn1.pdf}}
		\hfill
		\subfloat[]{\includegraphics[width=0.45\textwidth]{knn2.pdf}}
		\caption{Motivation for adaptively picking anchor points. In the two scenarios above, the same distribution of anchor points are given (represented by blue dots). The new data point to be estimated is shown as a red dot. Intuitively, in the left scenario it would be resonable to invole more anchor points in the local coding phase while in the right scenario considering fewer anchor points may relieve unreliable estimation of the membership of distint anchor points. In the conventional coding scheme, without loss of generality, fix $k = 8$, the surrounding anchor points range is denoted by green circle. Clearly, in the second scenairo, involving distant anchor points may lead to unreliable estimation of final prediction.}
	\end{figure}
	 Moreover, the anchor points pick and local coding are seperate phases in former localized soft-assignment coding. To address this issue, we propose a unified local coding  where the number of anchor points and local coding coordinate for each nearest anchor point are optimized in a joint fashion.

@@

	\begin{figure}[!tbp]
		\centering
		\subfloat[Magic04]{\includegraphics[width=0.5\textwidth]{magic04.pdf}}
		\hfill
		\subfloat[IJCNN]{\includegraphics[width=0.5\textwidth]{ijcnn.pdf}}
		\caption{Cumulative Hinge Loss in learning process on Magic04 and IJCNN dataset.}
	\end{figure}

	To illustrate the combination of supervised anchor point learning and optimum local coding coordinates learning, we give the average number of nearest neighbors learning curve in Figure 3. As the figure shows, the average number of anchor points involved in coding phase is decreasing and prone to converge. The reason may be that during the learning process, the anchor points are being optimized and gain more discriminative information of the whole dataset. These two methods contribute to a more stable and efficient online learning algorithm for locally linear classifiers.
	\begin{figure}[!tbp]
		\centering
		\subfloat[Magic04]{\includegraphics[width=0.5\textwidth]{magic04_nn.pdf}}
		\hfill
		\subfloat[IJCNN]{\includegraphics[width=0.5\textwidth]{ijcnn_nn.pdf}}
		\caption{Cumulative Average Number of Nearest Neighbors in learning process on Magic04 and IJCNN dataset.}
	\end{figure}

	\subsubsection{Evaluation of Parameter Sensitivity}
	For LLC-JO, Lipschitz to noise ratio $\mu$ is the key parameter. It would be interesting to explore how the algorithm may be sensitive to the setting of $\mu$. Figure 4 shows the results of parameter sensitive evaluations using different values of $\mu$. As $\mu$ grows, the number of anchor points involved in the coding phase tends to be smaller. There exists a range for $\mu$ that ensures LLC-JO outperforms LLC-SAPL, too small or too large $\mu$ will deteriorate the classification performance, which also proves that the number of anchor points involved in coding phase has a significant impact on localized soft-assignment coding scheme.

@@

		\includegraphics[width=0.8\textwidth]{magic04_mu.pdf}
		\caption{Sensitivity of Lipschitz to noise ratio on dataset Magic04. The red line indicates the average number of nearest neighbors in test data while the blue line denotes the test hingle loss in terms of different value of $\mu$. The black line denotes the corresponding test hinge loss of LLC-SAPL baseline.}

>>>>

\documentclass{llncs}
\usepackage[tbtags]{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{subfigure}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

@@

	Apart from local coding based methods, a number of other locally linear classifiers have been proposed. CSVM \cite{16} adopts K-means to partition the data into several clusters and then trains a linear SVM for each cluster. The key point of CSVM is that it requires each cluster's model to align with a global model, which can be treated as a kind of regularization. Different from CSVM, SVM-KNN \cite{17} employs a lazy learning strategy by training a linear SVM in the subregion of a testing sample and then use the trained SVM classifier for prediction.
	\section{Jointly Optimized Locally Linear Classifier}
	\subsection{Optimized Localized Soft-assignment Coding}
	Although localized soft-assignment coding  achieves a good balance between the local region constraint and sensitivity to the variance of distance, the number of nearest anchor points $k$ is commonly picked via cross-validation and fixed for the whole dataset. This strategy is based on the assumption that each data point shares similar local manifold. However, it is often the case that the dataset is generated from an unknown distribution which in turn leads to an unknown distributed anchor points, the local manifold may vary from data point to data point. In other words the optimum number of anchor points involved in the local coding is different for each data point as Figure 1 shows.
	\begin{figure*}[!htb]
		\centering
		\subfigure[]{\includegraphics[width=0.45\textwidth]{knn1.pdf}}
		\hfill
		\subfigure[]{\includegraphics[width=0.45\textwidth]{knn2.pdf}}
		\caption{Motivation for adaptively picking anchor points. In the two scenarios above, the same distribution of anchor points are given (represented by blue dots). The new data point to be estimated is shown as a red dot. Intuitively, in the left scenario it would be resonable to invole more anchor points in the local coding phase while in the right scenario considering fewer anchor points may relieve unreliable estimation of the membership of distint anchor points. In the conventional coding scheme, without loss of generality, fix $k = 8$, the surrounding anchor points range is denoted by green circle. Clearly, in the second scenairo, involving distant anchor points may lead to unreliable estimation of final prediction.}
	\end{figure*}
	 Moreover, the anchor points pick and local coding are seperate phases in former localized soft-assignment coding. To address this issue, we propose a unified local coding  where the number of anchor points and local coding coordinate for each nearest anchor point are optimized in a joint fashion.

@@

%	\begin{figure}[!tbp]
%		\centering
%		\subfloat[Magic04]{\includegraphics[width=0.5\textwidth]{magic04.pdf}}
%		\hfill
%		\subfloat[IJCNN]{\includegraphics[width=0.5\textwidth]{ijcnn.pdf}}
%		\caption{Cumulative Hinge Loss in learning process on Magic04 and IJCNN dataset.}
%	\end{figure}

	To illustrate the combination of supervised anchor point learning and optimum local coding coordinates learning, we give the average number of nearest neighbors learning curve in Figure 3. As the figure shows, the average number of anchor points involved in coding phase is decreasing and prone to converge. The reason may be that during the learning process, the anchor points are being optimized and gain more discriminative information of the whole dataset. These two methods contribute to a more stable and efficient online learning algorithm for locally linear classifiers.
	\begin{figure*}[!htb]
		\centering
		\subfigure[phishing]{
			\includegraphics[width=0.32\textwidth]{figs/phishing.pdf}
		}
		\subfigure[Magic04]{
			\includegraphics[width=0.32\textwidth]{figs/magic04.pdf}
		}
		\subfigure[IJCNN]{
			\includegraphics[width=0.32\textwidth]{figs/ijcnn.pdf}
		}
		\subfigure[w8a]{
			\includegraphics[width=0.32\textwidth]{figs/w8a.pdf}
		}
		\subfigure[connect-4]{
			\includegraphics[width=0.32\textwidth]{figs/connect4.pdf}
		}
		\subfigure[Covtype]{
			\includegraphics[width=0.32\textwidth]{figs/covtype.pdf}
		}
		\caption{Epoch-wise demonstration of different algorithms with hinge loss on test data}
		\label{allfig}
	\end{figure*}

	\begin{figure*}[!htb]
		\centering
		\subfigure[phishing]{
			\includegraphics[width=0.32\textwidth]{figs/phishing_nn.pdf}
		}
		\subfigure[Magic04]{
			\includegraphics[width=0.32\textwidth]{figs/magic04_nn.pdf}
		}
		\subfigure[IJCNN]{
			\includegraphics[width=0.32\textwidth]{figs/ijcnn_nn.pdf}
		}
		\subfigure[w8a]{
			\includegraphics[width=0.32\textwidth]{figs/w8a_nn.pdf}
		}
		\subfigure[connect-4]{
			\includegraphics[width=0.32\textwidth]{figs/connect4_nn.pdf}
		}
		\subfigure[Covtype]{
			\includegraphics[width=0.32\textwidth]{figs/covtype_nn.pdf}
		}
		\caption{Epoch-wise demonstration of LLC-DJO nn learning curve on test data}
		\label{allfig}
	\end{figure*}

	\subsubsection{Evaluation of Parameter Sensitivity}
	For LLC-JO, Lipschitz to noise ratio $\mu$ is the key parameter. It would be interesting to explore how the algorithm may be sensitive to the setting of $\mu$. Figure 4 shows the results of parameter sensitive evaluations using different values of $\mu$. As $\mu$ grows, the number of anchor points involved in the coding phase tends to be smaller. There exists a range for $\mu$ that ensures LLC-JO outperforms LLC-SAPL, too small or too large $\mu$ will deteriorate the classification performance, which also proves that the number of anchor points involved in coding phase has a significant impact on localized soft-assignment coding scheme.
	\begin{figure}[!tbp]
		\centering
		\includegraphics[width=0.8\textwidth]{figs/magic04_lip.pdf}
		\caption{Sensitivity of Lipschitz to noise ratio on dataset Magic04. The red line indicates the average number of nearest neighbors in test data while the blue line denotes the test hingle loss in terms of different value of $\mu$. The black line denotes the corresponding test hinge loss of LLC-SAPL baseline.}
	\end{figure}

@@

		\includegraphics[width=0.8\textwidth]{figs/anchor_points.pdf}
		\caption{anchor points number vs hingeloss}
